### 2022-11-15 chapters/interpretability/imli/experiment.tex
addressing reviewers comments

In Figure~\ref{interpretability_imli_fig:interpretable_classifiers}, we present results in an increasing number of samples in a dataset (from left to right).
In WDBC and Adult datasets presented on the first two plots in Figure~\ref{interpretability_imli_fig:interpretable_classifiers}, CORELS solves lower than $  600 $ instances within a timeout of $ 1000 $ seconds. The scalability performance of BRS is even worse, where it solves around $ 700 $ and $ 200 $ instances in WDBC and Adult datasets, respectively. The other three classifiers: {\imli}, BRL, and RIPPER  solve all $ 1000 $ instances, where BRL takes comparatively higher training time than the other two. The performance of {\imli} and RIPPER is similar, with RIPPER being comparatively better in the two datasets. However, the efficiency of {\imli} compared to other classifiers becomes significant as the number of samples in a dataset increases. In particular, in `Weather AUS' dataset, BRS cannot solve a single instance, BRL and CORELS solves $ ~400 $ instances, and RIPPER solves around $ 600 $ instances. {\imli}, however, solves all $ 1000 $ instances in this dataset. Similarly, in `BNG(labor)' dataset, all other classifiers except {\imli} and CORELS cannot solve any instance. While {\imli} mostly takes the maximum allowable time ($ 1000 $ seconds) in solving all instances in this dataset, CORELS can solve lower than $ 400 $ instances. 
Thus, {\imli} establishes itself as the most scalable classifier compared to other state-of-the-art interpretable classifiers.

>>>>

In Figure~\ref{interpretability_imli_fig:interpretable_classifiers}, we present results in an increasing number of samples in a dataset (from left to right).
In WDBC and Adult datasets presented on the first two plots in Figure~\ref{interpretability_imli_fig:interpretable_classifiers}, CORELS solves lower than $  600 $ instances within a timeout of $ 1000 $ seconds. The scalability performance of BRS is even worse, where it solves around $ 700 $ and $ 200 $ instances in WDBC and Adult datasets, respectively. The other three classifiers: {\imli}, BRL, and RIPPER  solve all $ 1000 $ instances, where BRL takes comparatively higher training time than the other two. The performance of {\imli} and RIPPER is similar, with RIPPER being comparatively better in the two datasets. However, the efficiency of {\imli} compared to other classifiers becomes significant as the number of samples in a dataset increases. In particular, in `Weather AUS' dataset, BRS cannot solve a single instance, BRL and CORELS solves $ ~400 $ instances, and RIPPER solves around $ 600 $ instances. {\imli}, however, solves all $ 1000 $ instances in this dataset. Similarly, in `BNG(labor)' dataset, all other classifiers except {\imli} and CORELS cannot solve any instance. While {\imli} mostly takes the maximum allowable time ($ 1000 $ seconds) in solving all instances in this dataset, CORELS can solve lower than $ 400 $ instances. \blue{The improved performance of {\imli} is due to incremental learning based on the novel integration of iterative learning and mini-batch learning. Contrary to our incremental learning, earlier approaches are based on heuristic rule-pruning (e.g., RIPPER) and rule-mining followed by Bayesian optimization (e.g., BRL, BRS) and branch and bounds algorithms (e.g., CORELS). Thus, owing to incremental learning, {\imli} establishes itself as the most scalable classifier compared to other state-of-the-art interpretable classifiers.}

### 2022-11-15 chapters/interpretability/imli/incremental_learning.tex
addressing reviewers comments

Our first improvement is to implement a mini-batch learning technique tailored for rule-based classifiers. Mini-batch learning has two-fold advantages. Firstly, instead of solving a large MaxSAT query for the whole training data, this approach solves a sequence of smaller MaxSAT queries derived from mini-batches of smaller size.  Secondly, this approach extends to life-long learning~\cite{chen2018lifelong}, where the classifier can be updated incrementally with new samples while also generalizing to previously observed samples. In our context of rule-based classifiers, we consider the following heuristic in mini-batch learning.

>>>>

Our first improvement is to implement a mini-batch learning technique tailored for rule-based classifiers. Mini-batch learning has two-fold advantages. Firstly, instead of solving a large MaxSAT query for the whole training data, this approach solves a sequence of smaller MaxSAT queries derived from mini-batches of smaller size.  \blue{Secondly, this approach extends to online learning, where the classifier can be updated incrementally with new samples while also generalizing to previously observed samples.} In our context of rule-based classifiers, we consider the following heuristic in mini-batch learning.
